### 2017-05-24 doc/manuscript.Rmd
Added Bernie's comments

Title: Specific clusters of fatty acids within the serum triacylglycerol fraction 
associate with the pathogenesis of type 2 diabetes

@@

**Objective**: 
Although elevated serum triglyceride (TAG) is a well-described risk factor for
type 2 diabetes (T2DM), few data are available regarding the role of the specific fatty
acid composition within serum TAG (TAGFA) in the pathogenesis of T2DM. Our aim, therefore, was to
examine longitudinal associations of TAGFA with insulin sensitivity (IS) and
beta-cell function.

@@

**Results**: 
The outcome variables declined by 14% to 27% over the 6-years. In the adjusted
GEE models, four TAGFA (14:0, 16:0, 14:1n-7, 16:1n-7 as mol%) had
strong negative associations with IS while others (e.g. 18:1n-7, 18:1n-9, 20:2n-6, 
20:5n-3) had strong positive associations. Few associations were seen for 
beta-cell function, except for 16:0 (negative) and 18:1n-7 (positive). PLS
analysis indicated four TAGFA (14:0, 16:0, 14:1n-7, 16:1n-7) that are markers of de novo lipogenesis (DNL)
clustered together and strongly predicted
lower IS. These four TAGFA also correlated highly (r>0.4) with clinically
measured TAG.

>>>>

Title: Specific clusters of fatty acids within the serum triacylglyceride fraction 
associate with the pathogenesis of type 2 diabetes

@@

**Objective**: 
Although elevated serum triacylglyceride (TAG) is a well-described risk factor for
type 2 diabetes (T2DM), few data are available regarding the role of the specific fatty
acid (FA) composition within serum TAG (TAGFA) in the pathogenesis of T2DM. Our aim, therefore, was to
examine longitudinal associations of TAGFA with insulin sensitivity (IS) and
beta-cell function.

@@

**Results**: 
The metabolic outcome variables declined by 14% to 27% over the 6-years. In the adjusted
GEE models, four TAGFA (14:0, 16:0, 14:1n-7, 16:1n-7 as mol%) had
strong negative associations with IS while others (e.g. 18:1n-7, 18:1n-9, 20:2n-6, 
20:5n-3) had strong positive associations. Few associations were seen for 
beta-cell function, except for 16:0 (negative) and 18:1n-7 (positive). PLS
analysis indicated four TAGFA (14:0, 16:0, 14:1n-7, 16:1n-7) that are markers of de novo lipogenesis (DNL)
clustered together and strongly predicted
lower IS. These four TAGFA also correlated highly (r>0.4) with clinically
measured TAG.
